EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-08-29 02_install.tex
Proofs update. Minor typos and tables fixed

\noindent
The CMake configuration can be further tuned using the following variables:
\begin{center}
\small
\begin{tabular}{ l|l|l } 
 \hline
  {\bf Option}               & {\bf Scope} & {\bf Value (default in {\color{xkcdEmerald}green})}\\
  \hline
  -D{\bf CMAKE\_INSTALL\_PREFIX}          & Install prefix override  & {\color{xkcdEmerald} None}\textbf{/}User-defined path \\

  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\\
  &&$\sim$/opt/edipack/custom \\
  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for each component are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

@@

\subsection{Environment Variables}\label{sSecInstallOSloading}
In order to avoid possible conflicts or the requirement for administrative
privileges, the results of the building step are installed by default in user's {\tt HOME}
directory.
As a consequence, the environment variables holding the library and include paths will need to be updated by the user.
We offer different ways to perform this action:
\begin{enumerate}
\item  A CMake-generated configuration file for an environment module which allows users to load and unload the library at any time. This is
  preferred solution for HPC systems. 
\item A CMake-generated bash script to be sourced (once or
  permanently) in any shell session to add \NAME library to the
  default environment.
\item A CMake-generated {\tt pkg-config} file to be added in
  the {\tt PKG\_CONFIG\_PATH} itself.  
\end{enumerate}
A recap message with all instructions is automatically generated at the end of the installation procedure.

>>>>

\noindent
The CMake configuration can be further tuned using the following
variables:
\begin{table}
\centering
\small
\begin{tabular}{ l|l|l } 
 \hline
  {\bf Option}               & {\bf Scope} & {\bf Value (default in {\color{xkcdEmerald}green})}\\
  \hline
  -D{\bf CMAKE\_INSTALL\_PREFIX}          & Install prefix override  & {\color{xkcdEmerald} None}\textbf{/}User-defined path \\

  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\\
  &&$\sim$/opt/edipack/custom \\
  -D{\bf USE\_MPI}       & MPI support  &  \textbf{/}{\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
 \hline
\end{tabular}
\caption{{\bf CMake optional flags}. The table lists the CMake
  optional flags available for the configuration step of the \NAME
  installation. Default variables are indicated in green.}
\label{Table1}
\end{table}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for each component are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

@@

\subsection{Environment Variables}\label{sSecInstallOSloading}
In order to avoid possible conflicts or the requirement for administrative
privileges, the results of the building step are installed by default
in the user's {\tt HOME}
directory.
As a consequence, the environment variables holding the library and include paths will need to be updated by the user.
We offer different ways to perform this action:
\begin{enumerate}
\item  A CMake-generated configuration file for an environment module
  which allows users to load and unload the library at any time. This
  is the preferred solution for HPC systems. 
\item A CMake-generated bash script to be sourced (once or
  permanently) in any shell session to add \NAME library to the
  default environment.
\item A CMake-generated {\tt pkg-config} file to be added in
  the {\tt PKG\_CONFIG\_PATH} itself.  
\end{enumerate}
A recap message with all instructions is automatically generated at the end of the installation procedure.

### 2025-08-29 03_edipack2.tex
Proofs update. Minor typos and tables fixed

\subsubsection{System setup}
We consider a quantum impurity system comprised by a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons. 
The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by the maximum  number of allowed phonons $N_\mathrm{ph}$, introducing a cutoff to the unbounded dimension of the local phonon Hilbert space.
The number of bath degrees of freedom $N_\mathrm{b}$ is a
function of the bath topology and of $N_\mathrm{bath}$, which is determined internally by \NAME.
For instance, for a simple case of a purely electronic problem, each bath
element corresponds to an independent electronic level coupled to the
impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
The total number of electronic levels in quantum impurity systems is indicated with $N_\mathrm{s}$.

@@

In \NAME, three different symmetry configurations 
controlled by the input variable {\tt ed\_mode} = {\bf normal}, 
{\bf superc}, {\bf nonsu2} are available. A summary of the sector properties is provided in
Table~(\ref{TabSector}).

@@

\begin{table}%[ht]
\begin{tabularx}{\linewidth}{ |X|X|X| }
 \hline
  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
  \hline
  {\bf normal} & $[N,S_z]\Leftrightarrow[N_\up,N_\dw]$ &
                                                $\binom{N_\mathrm{s}}{N_\up}\binom{N_\mathrm{s}}{N_\dw}$
  \\
  \hline
  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_\mathrm{s}-S_z-2m}\binom{N_\mathrm{s}}{N_\mathrm{s}-S_z-2m}\binom{S_z+2m}{m}$
  \\
  \hline
  {\bf nonsu2} & $N \equiv N_\up+N_\dw$ & $\binom{2N_\mathrm{s}}{N}$ \\ 
 \hline  
\end{tabularx}
\vspace{2mm}
\caption{\label{TabSector}
  {\bf Quantum Numbers}.
A table summarizing the possible values of the input variable {\tt
  ed\_mode} selecting the symmetries of the problem (first column). To each value
correspond different quantum numbers listed in the second column.
The third column reports the dimension of the electronic symmetry sector $\SS_{\vec{Q}}$ for a
given value of the quantum numbers $\vec{Q}$.}
\end{table}

@@

We summarize the total number $N_s$ of electronic levels of the quantum impurity system according to the value of $N_\a$, $N_\mathrm{bath}$ and the bath topology in the following table:
\begin{center}
\begin{tabular}{ |c||c|c|c|c| } 
 \hline     
{\tt bath\_type} & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
 \hline 
  \hline    
  $N_s$ & 
 $(N_\mathrm{bath}+1)N_\a$ & 
 $N_\mathrm{bath}+N_\a$ & 
 $N_\a(N_\mathrm{bath}+1)$ & 
 $N_\a(N_\mathrm{bath}+1)$  \\ 
 \hline
\end{tabular}
\end{center}

\vspace{2mm}
All the procedures concerning the bath
% , either on the user side or concerning the internal {\tt effective\_bath}, 
are grouped into a set of modules wrapped by {\tt ED\_BATH}. 
We divided the set of modules into three categories, according to their scope.

@@

The following table summarizes the total number of parameters $N_\mathrm{param}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:

\begin{center}
\begin{tabular}{ |c||c|c|c|c| } 
 \hline     
 $N_\mathrm{param}$ & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
 \hline 
 \hline    
 {\bf normal} & 
 $2N_\a N_\mathrm{bath}$ & 
 $(N_\a+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
 \hline
   {\bf superc} & $3N_\a N_\mathrm{bath}$ & 
 $(N_\a+2)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
 \hline
   {\bf nonsu2} & $3N_\a N_\mathrm{bath}$ & 
 $(2N_\a+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
 \hline
\end{tabular}
\end{center}

@@

The core computational task in any Krylov-based diagonalization
algorithm is the Matrix-Vector Product (MVP), i.e.~the application
of the Hamiltonian to a given input vector:
\begin{equation}
H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}.
\end{equation}
This operation amounts to more than 80\% of the overall
computational effort, making its optimization a critical aspect of
high-performance diagonalization algorithms. In Ref. \cite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling. 
Here, we provide a brief outline of the main ideas following the notation introduced
in Ref.~\onlinecite{Amaricci2022CPC}, and focusing on the impact of the choice of {\tt ed\_mode}. 
For sake of clarity, here we focus on the purely electronic case, i.e. neglecting the electron-phonon part. The product structure of the electron and phonon Fock spaces ensure that the following approach applies with few algorithmic modifications in presence of electron-phonon coupling.

@@

\subsection{Dynamical correlation functions}\label{sSecGF}
The determination of the low energy part of the Hamiltonian's spectrum
enables evaluation of the Dynamical Correlation Functions (DCFs) using Krylov subspace algorithm.
This capability is central to the library when using \NAME as an
impurity solver within the DMFT framework.

@@

To illustrate this approach, consider the normalized initial state
$$
\ket{\phi_n}=\AA^\dagger\ket{\psi_n}/\NN_n,
$$
where  $\ket{\psi_n}\in\SS_{\vec{Q}}$ is an eigenstate of the sector Hamiltonian and $\NN_n=\sqrt{\bra{\psi_n}\AA
  \AA^\dagger\ket{\psi_n}}$.
The Krylov basis is constructed by repeated applications of the sector Hamiltonian via MVP: 
$$
\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
\}
$$ 
with $1 \ll N \ll \DD_\SS$.
Given that any eigenstate $\ket{\psi_n}$ can be expressed within the Krylov basis as
$$
\ket{\psi_n} = \sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
\sum_i a^n_i \ket{v^n_i}, 
$$
we can approximate the expression \equ{KLgf} as:  
\begin{equation}
  \label{eqGKrylov}
  \begin{split}
    C_\AA(z)  &\simeq \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^\dagger\ket{\psi_n} |a^n_m|^2}{
      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^\dagger \AA\ket{\psi_n}
      |a^n_m|^2}{ z + (E_m-E_n)}\cr
    %
    &= \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}}\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
    \equiv \frac{1}{\tilde{Z}}\sum_n
    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn}), \cr
  \end{split}
\end{equation}
where the terms are grouped as a sum over spectral weights and
poles. We introduced the notation $g(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn})$
for the {\tt gfmatrix} object containing the weights $w^{\nu}_{mn}(\AA)$ and
poles $dE^{\nu}_{mn}(\AA)$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
contributing to the low energy spectrum, for every order $m$ of the
Krylov subspace algorithm and for channel $\nu$.
% This approach significantly reduces the computational burden, as it
% requires a much smaller set of basis states.

@@

For sake of simplicity, this section focuses on the zero-temperature limit, 
assuming a non-degenerate ground state $\ket{\psi}$ present in the 
{\tt state\_list}. The generalization to the finite-temperature regime 
or degenerate ground states is straightforward, requiring only the  introduction of an
ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
\equ{eq:thermal_average}.

>>>>

\subsubsection{System setup}
We consider a quantum impurity system comprised of a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons. 
The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by the maximum  number of allowed phonons $N_\mathrm{ph}$, introducing a cutoff to the unbounded dimension of the local phonon Hilbert space.
The number of bath degrees of freedom $N_\mathrm{b}$ is a
function of the bath topology and of $N_\mathrm{bath}$, which is determined internally by \NAME.
For instance, for a simple case of a purely electronic problem, each bath
element corresponds to an independent electronic level coupled to the
impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
The total number of electronic levels in quantum impurity systems is indicated with $N_\mathrm{s}$.

@@

In \NAME, three different symmetry configurations 
controlled by the input variable {\tt ed\_mode} = {\bf normal}, 
{\bf superc}, {\bf nonsu2} are available. A summary of the sector properties is provided in
Table~(\ref{Table2}).

@@

\begin{table}
  \centering
  \begin{tabular}{ |c|c|c| }
 \hline
  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
  \hline
  {\bf normal} & $[N,S_z]\Leftrightarrow[N_\up,N_\dw]$ &
                                                $\binom{N_\mathrm{s}}{N_\up}\binom{N_\mathrm{s}}{N_\dw}$
  \\
  \hline
  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_\mathrm{s}-S_z-2m}\binom{N_\mathrm{s}}{N_\mathrm{s}-S_z-2m}\binom{S_z+2m}{m}$
  \\
  \hline
  {\bf nonsu2} & $N \equiv N_\up+N_\dw$ & $\binom{2N_\mathrm{s}}{N}$ \\ 
 \hline  
\end{tabular}
\caption{
 {\bf Quantum Numbers}.
A table summarizing the possible values of the input variable {\tt
  ed\_mode} selecting the symmetries of the problem (first column). To each value
correspond different quantum numbers listed in the second column.
The third column reports the dimension of the electronic symmetry sector $\SS_{\vec{Q}}$ for a
given value of the quantum numbers $\vec{Q}$.}
\label{Table2}
\end{table}

@@

We summarize the total number $N_s$ of electronic levels of the
quantum impurity system according to the value of $N_\a$,
$N_\mathrm{bath}$ and the bath topology in Table~\ref{Table3}:

\begin{table}
\centering
\begin{tabular}{ |c||c|c|c|c| } 
 \hline     
{\tt bath\_type} & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
 \hline 
  \hline    
  $N_s$ & 
 $(N_\mathrm{bath}+1)N_\a$ & 
 $N_\mathrm{bath}+N_\a$ & 
 $N_\a(N_\mathrm{bath}+1)$ & 
 $N_\a(N_\mathrm{bath}+1)$  \\ 
 \hline
\end{tabular}
\caption{
  {\bf Total number of electronic levels}.
  The table summarizes the possible number of the electronic levels $N_s$ (second row) according to the value of the {\tt bath\_type}
(first row), the number of impurity orbitals $N_\alpha$ and the number
of the bath sites $N_{\rm bath}$.}
\label{Table3}
\end{table}

% \vspace{2mm}
All the procedures concerning the bath
% , either on the user side or concerning the internal {\tt effective\_bath}, 
are grouped into a set of modules wrapped by {\tt ED\_BATH}. 
We divided the set of modules into three categories, according to their scope.

@@

Table~\ref{Table4} summarizes the total number of parameters $N_\mathrm{param}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:

\begin{table}
\centering
\begin{tabular}{ |c||c|c|c|c| } 
 \hline     
 $N_\mathrm{param}$ & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
 \hline 
 \hline    
 {\bf normal} & 
 $2N_\a N_\mathrm{bath}$ & 
 $(N_\a+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
 \hline
   {\bf superc} & $3N_\a N_\mathrm{bath}$ & 
 $(N_\a+2)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
 \hline
   {\bf nonsu2} & $3N_\a N_\mathrm{bath}$ & 
 $(2N_\a+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
 $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
 \hline
\end{tabular}
\caption{
  {\bf Total number of bath parameters}. The table lists the number of
  bath parameters $N_{\rm param}$ according to the conserved
  symmetry {\tt ed\_mode} (first column), and the
  bath topology {\tt bath\_type} (first
  row). The number of parameters is obtained as a function of the
  impurity orbitals $N_\alpha$, the number of spin channels
  $N_\sigma$, the number of bath sites $N_{\rm bath}$ and, where
  applicable, the size of the matrix basis used to describe the {\tt
    replica/general} bath structure $N_{\rm sym}$.}
\label{Table4}
\end{table}

@@

The core computational task in any Krylov-based diagonalization
algorithm is the Matrix-Vector Product (MVP), i.e.~the application
of the Hamiltonian to a given input vector:
\begin{equation}
H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}.
\end{equation}
This operation amounts to more than 80\% of the overall
computational effort, making its optimization a critical aspect of
high-performance diagonalization algorithms. In Ref. \cite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling. 
Here, we provide a brief outline of the main ideas following the notation introduced
in Ref.~\onlinecite{Amaricci2022CPC}, and focusing on the impact of the choice of {\tt ed\_mode}. 
For the sake of clarity, here we focus on the purely electronic case, i.e. neglecting the electron-phonon part. The product structure of the electron and phonon Fock spaces ensure that the following approach applies with few algorithmic modifications in presence of electron-phonon coupling.

@@

\subsection{Dynamical correlation functions}\label{sSecGF}
The determination of the low-energy part of the Hamiltonian's spectrum
enables evaluation of the Dynamical Correlation Functions (DCFs) using Krylov subspace algorithm.
This capability is central to the library when using \NAME as an
impurity solver within the DMFT framework.

@@

To illustrate this approach, consider the normalized initial state
$$
\ket{\phi_n}=\AA^\dagger\ket{\psi_n}/\NN_n,
$$
where  $\ket{\psi_n}\in\SS_{\vec{Q}}$ is an eigenstate of the sector Hamiltonian and $\NN_n=\sqrt{\bra{\psi_n}\AA
  \AA^\dagger\ket{\psi_n}}$.
The Krylov basis is constructed by repeated applications of the sector Hamiltonian via MVP: 
$$
\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
\}
$$ 
with $1 \ll N \ll \DD_\SS$.
Given that any eigenstate $\ket{\psi_n}$ can be expressed within the Krylov basis as
$$
\ket{\psi_n} = \sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
\sum_i a^n_i \ket{v^n_i}, 
$$
we can approximate the expression \equ{KLgf} as:  
\begin{equation}
  \label{eqGKrylov}
  \begin{split}
    C_\AA(z)  &\simeq \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^\dagger\ket{\psi_n} |a^n_m|^2}{
      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^\dagger \AA\ket{\psi_n}
      |a^n_m|^2}{ z + (E_m-E_n)}\cr
    %
    &= \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}}\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
    \equiv \frac{1}{\tilde{Z}}\sum_n
    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn}), \cr
  \end{split}
\end{equation}
where the terms are grouped as a sum over spectral weights and
poles. We introduced the notation $g(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn})$
for the {\tt gfmatrix} object containing the weights $w^{\nu}_{mn}(\AA)$ and
poles $dE^{\nu}_{mn}(\AA)$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
contributing to the low-energy spectrum, for every order $m$ of the
Krylov subspace algorithm and for channel $\nu$.
% This approach significantly reduces the computational burden, as it
% requires a much smaller set of basis states.

@@

For the sake of simplicity, this section focuses on the zero-temperature limit, 
assuming a non-degenerate ground state $\ket{\psi}$ present in the 
{\tt state\_list}. The generalization to the finite-temperature regime 
or degenerate ground states is straightforward, requiring only the  introduction of an
ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
\equ{eq:thermal_average}.

### 2025-08-29 04_cbinding.tex
Proofs update. Minor typos and tables fixed

\subsubsection{Implementation}\label{sSecInteropCbindingsImplementation}
The interface layer is contained in the Fortran module {\tt
  EDIPACK\_C}. It contains a common part and two set of functions,
one to interface the procedures from \NAME and a second
one to extend the interface to the inequivalent impurities case.
Specifically, the implemented interface functions expose to C through
{\tt bind(C)} statement a number of
procedures composing the Fortran API of \NAME, i.e. contained in {\tt
  ED\_MAIN}. The procedures and shared variables can be divided in four main groups (note that contrary to the Fortran API the functions here lose the prefix {\tt ed\_}):

@@

\subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
\paragraph{From source.}
EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
The code can be obtained and and installed from source as:
\begin{lstlisting}[style=mybash]
git clone https://github.com/edipack/EDIpack2py EDIpack2py
cd EDIpack2py
pip install . 
\end{lstlisting}

@@

\noindent
When the {\tt EDIpack2py}    module is imported, it attempts to load the dynamic library {\tt
  libedipack\-\_cbindings.so (.dylib)} containing the Fortran-C bindings
for \NAME. By default the library search proceeds as follow: 
\begin{enumerate}
\item The user can override the location of the library
  (determined during the \NAME build configuration) by exporting an
  environment variable called {\tt EDIPACK\_PATH}.
\item By default, the Python module detects the location of the
  Fortran libraries via {\tt pkg-config}. Any of the loading methods
  outlined in \secu{sSecInstallOSloading} automatically pushes the
  correct configuration to {\tt PKG\_CONFIG\_PATH}. 
\item As a last resort, the environment variables {\tt
    LD\_LIBRARY\_PATH} and {\tt DYLD\_LIBRARY\_PATH} are analyzed to
  retrieve the correct location. 
\end{enumerate}
If none of the previous attempts succeeds, the module will not load correctly and an error message will be printed.

>>>>

\subsubsection{Implementation}\label{sSecInteropCbindingsImplementation}
The interface layer is contained in the Fortran module {\tt
  EDIPACK\_C}. It contains a common part and two sets of functions,
one to interface the procedures from \NAME and a second
one to extend the interface to the inequivalent impurities case.
Specifically, the implemented interface functions expose to C through
{\tt bind(C)} statement a number of
procedures composing the Fortran API of \NAME, i.e. contained in {\tt
  ED\_MAIN}. The procedures and shared variables can be divided in four main groups (note that contrary to the Fortran API the functions here lose the prefix {\tt ed\_}):

@@

\subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
\paragraph{From source.}
EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
The code can be obtained and installed from source as:
\begin{lstlisting}[style=mybash]
git clone https://github.com/edipack/EDIpack2py EDIpack2py
cd EDIpack2py
pip install . 
\end{lstlisting}

@@

\noindent
When the {\tt EDIpack2py}    module is imported, it attempts to load the dynamic library {\tt
  libedipack\-\_cbindings.so (.dylib)} containing the Fortran-C bindings
for \NAME. By default the library search proceeds as follows: 
\begin{enumerate}
\item The user can override the location of the library
  (determined during the \NAME build configuration) by exporting an
  environment variable called {\tt EDIPACK\_PATH}.
\item By default, the Python module detects the location of the
  Fortran libraries via {\tt pkg-config}. Any of the loading methods
  outlined in \secu{sSecInstallOSloading} automatically pushes the
  correct configuration to {\tt PKG\_CONFIG\_PATH}. 
\item As a last resort, the environment variables {\tt
    LD\_LIBRARY\_PATH} and {\tt DYLD\_LIBRARY\_PATH} are analyzed to
  retrieve the correct location. 
\end{enumerate}
If none of the previous attempts succeeds, the module will not load correctly and an error message will be printed.

### 2025-08-29 05_examples.tex
Proofs update. Minor typos and tables fixed

\item Use the dedicated
  input/output \NAME procedures to retrieve the self-energy functions  
  $\hat{\Sigma}(i\omega)$ and $\hat{S}(i\omega)$ on the 
  Matsubara axis.

>>>>

\item[{\tiny {\bf EDIpack}}]  Use the dedicated
  input/output \NAME procedures to retrieve the self-energy functions  
  $\hat{\Sigma}(i\omega)$ and $\hat{S}(i\omega)$ on the 
  Matsubara axis.
